Advances in Artificial Intelligence for Data Visualization: Developing Computer Vision Models to Automate Reading of Data Plots, with Application to Predictive Model Diagnostics

### 2024-08-11 Thesis/03-chap3.qmd
update the compiled version

```{r fig-delta, fig.pos = "!h", fig.cap = "A weighted detection rate vs adjusted $\\delta$-difference plot. The brown line is smoothing curve produced by fitting gnealized additive models", fig.height = 4}
experiment %>%
  left_join(lineup_vss %>%
              group_by(unique_lineup_id) %>%
              summarise(delta_diff = first(delta_diff), gamma_diff = first(gamma_diff))) %>%
  ggplot() +
  geom_vline(xintercept = 0, alpha = 0.4, linetype = 2) +
  geom_point(aes(delta_diff, prop_detect), alpha = 0.3) +
  geom_smooth(aes(delta_diff, prop_detect), se = FALSE, col = "#994F00") +
  ylab("Weighted detection rate") +
  xlab(expression(delta[adj])) +
  theme_light()
```

>>>>

```{r fig-delta, fig.pos = "!h", fig.cap = "A weighted detection rate vs adjusted $\\delta$-difference plot. The brown line is smoothing curve produced by fitting gnealized additive models.", fig.height = 4}
experiment %>%
  left_join(lineup_vss %>%
              group_by(unique_lineup_id) %>%
              summarise(delta_diff = first(delta_diff), gamma_diff = first(gamma_diff))) %>%
  ggplot() +
  geom_vline(xintercept = 0, alpha = 0.4, linetype = 2) +
  geom_point(aes(delta_diff, prop_detect), alpha = 0.3) +
  geom_smooth(aes(delta_diff, prop_detect), se = FALSE, col = "#994F00") +
  ylab("Weighted detection rate") +
  xlab(expression(delta[adj])) +
  theme_light()
```
